Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-07-02 large_experiment_processing.Rmd
Update large_experiment_processing.Rmd
Co-authored-by: Sebastian Gibb <mail@sebastiangibb.de>

Before evaluating the `MSnbase` performance on the large data set we provide
some general description of the `MSnbase` data classes and basic
data access operations. MS data from raw data files in mzML, mzXML, mzData or
netCDF format is represented by the `MSnExp` object which organizes the spectra
from the original files in an one-dimensional list. Functions like `rtime` and
`msLevel` allow to extract the retention time and MS level, respectively.
They return a `numeric` (or `integer`) vector with the same length
than the number of spectra in the `MSnExp`. In the example below we use the
`rtime` function to extract the retention times for each spectrum.

@@

In addition, it is also possible to extract all m/z and intensity values from an
`MSnExp` object as a `data.frame` as shown in the code block below, but this is
not suggested, since it loads all the data into memory and all MS spectrum
metadata such as MS level or precursor m/z get lost.

>>>>

Before evaluating the `MSnbase` performance on the large data set we provide
some general description of the `MSnbase` data classes and basic
data access operations. MS data from raw data files in mzML, mzXML, mzData or
netCDF format is represented by the `MSnExp` object which organizes the spectra
from the original files in an one-dimensional list. Functions like `rtime` and
`msLevel` allow to extract the retention time and MS level, respectively.
They return a `numeric` (or `integer`) vector with the same length
as the number of spectra in the `MSnExp`. In the example below we use the
`rtime` function to extract the retention times for each spectrum.

@@

In addition, it is also possible to extract all m/z and intensity values from an
`MSnExp` object as a `data.frame` as shown in the code block below, but this is
not suggested, since it loads all the data into memory but all MS spectrum
metadata such as MS level or precursor m/z get lost.
